---
title: "README"
output: html_document
---

##Pre-step
- Download the data set from https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
- Unzip the data into your working directory
- Install "reshape2" package

##1st-step
- Read relevant train and test dataset and merge them into **raw_data**
```{r,eval=FALSE}
current <- getwd()
setwd("UCI HAR Dataset")
current2 <- getwd()
setwd("train")
subject_train <- read.table("subject_train.txt")
train <- read.table("X_train.txt")
activity_train <- read.table("y_train.txt")
data_train <- data.frame(subject_train,activity_train,train)
setwd(current2)
setwd("test")
subject_test <- read.table("subject_test.txt")
test <- read.table("X_test.txt")
activity_test <- read.table("y_test.txt")
data_test <- data.frame(subject_test,activity_test,test)
raw_data <- rbind(data_train,data_test)
```

##2nd-step
- Extract mean and standard deviation data column for each measurement, become **extracted_data**
```{r,eval=FALSE}
setwd(current2)
raw_name <- as.vector(read.table("features.txt")[,2])
col_label <- c("subject","activity",raw_name)
check <- grepl("mean\\(\\)|std\\(\\)",col_label)
extracted_data <- data.frame(raw_data[,1:2],raw_data[,check])
```

##3rd-step
- Cooperate activity names into the data set, with sorting sequences on subject and activity, become **factored_data**
```{r,eval=FALSE}
activity_labels <- as.vector(read.table("activity_labels.txt")[,2])
arrangement <- order(extracted_data[,1],extracted_data[,2])
sorted_data <- extracted_data[arrangement,]
hold <- rep("a",nrow(sorted_data))
for(i in 1:nrow(sorted_data)){
  hold[i] <- activity_labels[sorted_data[i,2]]
}
factored_data <- data.frame(sorted_data[,1],hold,sorted_data[3:ncol(sorted_data)])
```

##4th-step
- Apply column names into **factored_data**
```{r,eval=FALSE}
factored_name <- col_label[check]
colnames(factored_data) <- c("subject","activity",factored_name)
```

##5th-step
- Rearrange and melt the datasets to form a tidy data set to export as **tidy data.txt**
```{r,eval=FALSE}
total_subject <- length(unique(factored_data[,1]))
total_activity <- length(activity_labels)
subject <- vector()
row <- total_subject*total_activity
col <- sum(check)
tidy_matrix <- matrix(nrow=row,ncol=col)
for(i in 1:total_subject){
  subject <- cbind(subject,rep(i,6))
  for(j in 1:total_activity){
    temp <- data.frame()
    select <- (factored_data[,1]==i & factored_data[,2]==activity_labels[j])
    temp <- factored_data[select,]
    for(k in 1:ncol(tidy_matrix)){
      x <- 6*(i-1)+j
      tidy_matrix[x,k] <- mean(temp[,k+2])
    }
  }
}
subject <- as.vector(subject)
activity <- rep(activity_labels,total_subject)
tidy_name <- paste("average_of_",factored_name,sep="")
tidy_data <- data.frame(subject,activity,tidy_matrix)
colnames(tidy_data) <- c("subject","activity",tidy_name)
library(reshape2)
data_melt <- melt(tidy_data,id=c("subject","activity"),measure.vars=tidy_name)
setwd(current)
write.table(data_melt,"tidy data.txt",row.names=FALSE,quote=FALSE)
```